---
title: |
  <center> CHAD Output Summary </center>
subtitle: |
  <center> `r format(Sys.time(), '%d %B, %Y')` </center>
  
author: 
date:
output: html_document
params:
    radius: NA
    base: NA
    pjDays: NA
    socDis: NA

---


---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo = FALSE, warning = FALSE, message = FALSE}
# Some global stuff
library(ggplot2)
library(plotly)
library(knitr)
library(kableExtra)

Counties = GetCounties(params$base, params$radius)
Hospitals = GetHospitals(params$base, params$radius)
CountyDT = GetLocalDataTable(Counties)
CovidCounties = subset(CovidConfirmedCases, CountyFIPS %in% Counties$FIPS)
CountyCovid = CalculateCovid(Counties)
CountyDeaths = CalculateDeaths(Counties)
TotPop = CalculateCounties(Counties)
CovidCaseChng = sum(rev(CovidCounties)[,1] - rev(CovidCounties)[,2])
CovidDeathChng <- sum(rev(CovidCounties)[,1] - rev(CovidCounties)[,2])
HospUltz = HospitalIncreases(Counties, Hospitals)
```
---





<center>
#  Base: `r params$base` 
</center>

The Air Force COVID-19 Health Assessment Dashboard (CHAD) was developed to provide a centralized location for leadership to receive up-to-date pandemic information specifically tailored to their installation and the surrounding local area. 

This report was generated using a **`r params$radius` mile radius** around **`r params$base`** as the defined local area.




## Current Local Area Info

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

<div class = "row">

<div class = "col-md-4">

- Local Population: `r TotPop`

- Total Local Cases: `r comma(CalculateCovid(Counties))`

- New Local Cases: `r paste("+",toString(CovidCaseChng))`

- Total Local Fatalities: `r comma(CalculateDeaths(Counties))`

- New Local Fatalities: `r paste("+",toString(CovidDeathChng))`

- Local Hospital Bed Utilization: `r HospUltz`

- Local Hospital Bed Utilization Change: 

</div>

<div class = "col-md-8">

```{r fig.height = 4, fig.width = 5, echo=FALSE}
CountyChoro = PlotLocalChoro(Counties, params$base, "County")
CountyChoro
```

</div>
</div>

## Local Area Plots

<br>

### Daily Stats

The charts below display the 

<div class = "row">

<div class = "col-md-6">
```{r fig.height = 4, fig.width = 4, echo=FALSE}
CCDaily = CovidCasesPerDayChart(params$base, params$radius, Counties, Hospitals)
CCDaily = CCDaily %>% layout(xaxis = list(showgrid = T),
                             yaxis = list(showgrid = T))
CCDaily
```
</div>

<div class = "col-md-6">
```{r fig.height = 4, fig.width = 4, echo=FALSE}
CCtot = CovidCasesCumChart(params$base, params$radius, Counties, Hospitals)
CCtot = CCtot %>% layout(xaxis = list(showgrid = T),
                         yaxis = list(showgrid = T))
CCtot
```
</div>

</div>



### Detailed County Info

The table displays information for each county in `r params$radius` of `r params$base`.


```{r echo=FALSE}
kable(CountyDT) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```



### Local Projections

This section will display the projections from the IHME model and CHIME inspired model

#### Overlay

```{r fig.height = 5, fig.width = 10,echo=FALSE}
overlay = PlotOverlay(params$base, 
                      Counties, 
                      Hospitals, 
                      params$socDis, 
                      params$pjDays,
                      "Hospitalizations")
overlay
```





